\chapter{Introduction} \label{cp:intro} %Patricia
In recent years, Small Unmanned Aircraft Systems (SUAS), commonly known as drones, have emerged as a significant security threat to United States citizens and national infrastructure. These threats include hostile surveillance, espionage, smuggling of illegal payloads, Global Positioning System (GPS) spoofing, signal jamming, and weaponization. The increasing misuse of drones for illicit activities underscores the critical need for effective countermeasures to safeguard sensitive areas from these airborne threats.

To address this challenge, the Department of Homeland Security (DHS) has issued a solicitation for prototype development aimed at creating an Unmanned Aerial Vehicle (UAV) capable of detecting and neutralizing hostile SUAS. In response, StratoShield has designed an aircraft, \textit{The Banshee}, equipped with technology to detect and jam SUAS control signals. \textit{The Banshee} will be capable of patrolling an Area of Interest (AOI) for up to 45 minutes, ensuring the protection of buildings and individuals in the area. The primary mission objective is to identify and disable SUAS threats using non-destructive electronic countermeasures.


\section{Overview of Mission} %Patricia
The mission has several requirements, ranging from customer-driven needs to business-driven constraints. The following list outlines the high-level requirements that define the mission’s scope and purpose:

\begin{enumerate}
    \item The UAV shall prevent a hostile airborne Small Unmanned Aircraft System (SUAS) from reaching a key area in an Area of Interest (AOI).
    \item The UAV shall be equipped with equipment capable of jamming a SUAS and equipment capable of detecting a hostile SUAS.
    \item The UAV shall be capable of completing a full no-engagement flight cycle of at least 45 minutes.
    \item The UAV shall be capable of fixed-wing flight, have a maximum Gross Take-Off Weight (GTOW) of 12 lb, and have a maximum wingspan of 90 in.
\end{enumerate}

Given the demanding endurance and physical requirements, the primary focus of the design process was maximizing The Banshee’s efficiency and flight time while adhering to physical and budgetary constraints.


% Provide a brief description/overview of the mission

\section{Report Organization}

% Provide a high-level overview of where the reader could find relevant information.
